Fluent statistical computing interfaces for biological data analysis

### 2020-03-23 Rmd/05-embeddings.Rmd
update bib

<!--
- review of embedding algorithms, interactive graphics, tours
- technology
- design
- examples/benchmarks
  - Kevin moon
  - pdfsense
  - single cell
  - quick draw
https://jlmelville.github.io/smallvis/init.html#other_initialization_options
-->

>>>>

<!--
- review of embedding algorithms, interactive graphics, tours
- technology
- design
- examples/benchmarks
  - Kevin moon
  - single cell
https://jlmelville.github.io/smallvis/init.html#other_initialization_options
-->
